Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
updates

As our paper is about the 2024 United States federal election and more specifically we are looking at the polling Data and the polling data comparing the two candidates, former President Donald Trump and Vice President Kamala Harris, for the upcoming election. Our original Data set had over 16,000 unique entries from different pollsters, the business or Organization that conducts the poll. Each poll has two entries, one giving the Data for the polling opinions of Donald Trump and the second for Kamala Harris. We have acquired our polling data from @fivethirtyeight2024

@@

n predictive modeling, accounting for pollster variability and methodology is essential to avoid overfitting to any single source. By including pollster as a predictor in the model, we allow it to recognize that poll results may vary not only due to real changes in public opinion but also because of differences in survey methodologies. This consideration enables the model to generate more accurate, generalized predictions, offering a reliable forecast that reflects a well-rounded view of public opinion

@@

@@

@@

Although there are both advatages and disadvantages, we feel that this survey is well though out and doesn't allow for ambiguity in the answers of the participants.

>>>>

As our paper is about the 2024 United States federal election and more specifically we are looking at the polling Data and the polling data comparing the two candidates, former President Donald Trump and Vice President Kamala Harris, for the upcoming election. Our original Data set had over 16,000 unique entries from different pollsters, the business or Organization that conducts the poll. Each poll has two entries, one giving the Data for the polling opinions of Donald Trump and the second for Kamala Harris. We have acquired our polling data from @fivethirtyeight2024.

@@

In predictive modeling, accounting for pollster variability and methodology is essential to avoid overfitting to any single source. By including pollster as a predictor in the model, we allow it to recognize that poll results may vary not only due to real changes in public opinion but also because of differences in survey methodologies. This consideration enables the model to generate more accurate, generalized predictions, offering a reliable forecast that reflects a well-rounded view of public opinion.

@@

The Bayesian model we employ leverages probabilistic reasoning to predict Kamala Harris's support across different states. Bayesian models offer a flexible framework for incorporating prior information alongside observed data to produce posterior distributions, which reflect updated opinions based on the data. This model was chosen for its ability to incorporate prior knowledge, handle uncertainty, and generate predictions that can adapt to the polling data, providing a more comprehensive forecast of Harris’s support across swing states.

@@

The last swing state we will be discussing is Wisconsinng which we can see in our prediction table, @tbl-supporttable, has the high support at 48.38% for Harris from all this swing states we looked at. when we look at @fig-supportWP, se a small spike in early september for Harris, followed by a gradual stabilization at around 48% support for Harris similar to what our model shows. Now if we also take into ac count @fig-supportstate, we see that Wisconsin has the largest difference in support for Harris in comparison to all previously mentioned swing states.

Lastly, if we look at Wisconsin's voting history, the only time Wisconsin voted Republican since 1988 was in 2016 when the state gave its electoral votes for Trump with 47.2% of the vote to Clinton's 46.5. then in 2020 the state went back to blue with Biden winning the state, allt hings considered out of all states we took into account Harris is likely to win.

We believe Wisconsin will vote: **Kamala Harris**

## Electoral Vote Projection and Predicted Outcome

Without considering the swing states and if we assume all the other states will vote as expected Kamala Harris has a slight lead of 226 electoral votes to Donald Trump's 219. Now, if we take the 43 combined votes of Arizona, Georgia, and North Carolina, and add it to Trumps tally. While allocate Nevada, Michigan, Pennsylvania, and Wisconsin's votes to Harris which sum up to 50 electoral votes. This totals to a Democratic victory for Kamala Harris at 276 votes to Donald Trump's 262, we have come to the conclusion that Kamala Harris is likely to win the upcomming United States election by 14 electoral votes.

@@

Although there are both advantages and disadvantages, we feel that this survey is well though out and doesn't allow for ambiguity in the answers of the participants.
